%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}
\label{preface}

The body of this thesis is composed of three separate studies that have all been published in peer-reviewed journals. They have been subject to minor edits to fit with the required form of this thesis. 

\autoref{ch2} is an adaptation of the article -- {\it Magnification by Galaxy Group Dark Matter Halos} by J. Ford, H. Hildebrandt, L. Van Waerbeke, A. Leauthaud, P. Capak, A. Finoguenov, M. Tanaka, M. R. George, and J. Rhodes, published in The Astrophysical Journal, Volume 754, Issue 2, article id. 143, 6 pp. (2012). The author of this thesis led the analysis, performed all calculations, wrote all code used in the work, and drafted the published manuscript. H. Hildebrandt and L. Van Waerbeke (thesis advisor) provided regular discussions and guidance that shaped the formulation of the research. A. Leauthaud and P. Capak provided data and astronomical catalogs for analysis. All authors gave comments and edits on the final manuscript.

\autoref{ch3} is an adaptation of the article -- {\it Cluster Magnification and the Mass-Richness Relation in CFHTLenS} by J. Ford, H. Hildebrandt, L. Van Waerbeke, T. Erben, C. Laigle, M. Milkeraitis, and C. B. Morrison, published in Monthly Notices of the Royal Astronomical Society, Volume 439, Issue 4, p.3755-3764 (2014). The author of this thesis led the analysis, performed all calculations, wrote or heavily modified all code used in the work, and drafted the published manuscript. H. Hildebrandt and L. Van Waerbeke (thesis advisor) provided regular discussions and guidance that shaped the formulation of the research. T. Erben was heavily involved in producing the CFHTLenS data products used in this work. C. Laigle wrote the first version of the code for calculating cluster richness, which was adapted by the thesis author for this work. M. Milkeraitis compiled the 3D-Matched-Filter galaxy cluster catalog. C. B. Morrison performed a study of Lyman-break galaxy low-redshift contamination, upon which this manuscript relied. All authors gave comments and edits on the final manuscript.

\autoref{ch4} is an adaptation of the article -- {\it CFHTLenS: A Weak Lensing Shear Analysis of the 3D-Matched-Filter Galaxy Clusters} by J. Ford, L. Van Waerbeke, M. Milkeraitis, C. Laigle, H. Hildebrandt, T. Erben, C. Heymans, H. Hoekstra, T. Kitching, Y. Mellier, L. Miller, A. Choi, J. Coupon, L. Fu, M. J. Hudson, K. Kuijken, N. Robertson, B. Rowe, T. Schrabback, and M. Velander, published in Monthly Notices of the Royal Astronomical Society, Volume 447, Issue 2, p.1304-1318 (2015). The author of this thesis led the analysis, performed all calculations, wrote or heavily modified all code used in the work, and drafted the published manuscript. The authorship list reflects the lead authors of this paper followed by two alphabetical groups. L. Van Waerbeke (thesis advisor) and H. Hildebrandt provided regular discussions and guidance that shaped the formulation of the research. M. Milkeraitis compiled the 3D-Matched-Filter galaxy cluster catalog which was analyzed. C. Laigle wrote the first version of the code for calculating cluster richness, which was later adapted by the thesis author for this work. The next group includes key contributors to the science analysis and interpretation in this paper, the founding core team and those whose long-term significant effort produced the final CFHTLenS data product. The final group covers members of the CFHTLenS team who made a significant contribution to the project and/or this paper. All authors gave comments and edits on the final manuscript.

